Predicting detection probabilities for rare and undersampled North American landbirds

### 2023-10-04 article/article.tex
added more to methods and added bibliography

@@

\subsection{Bayesian Hierarchical QPAD Removal Model}

@@

\subsection{Bayesian Hierarchical QPAD Distance Model}

@@

>>>>

\subsection{Data Collection}
\subsubsection{Point Count Data}
\par We used the same standardized database of point count data that was put together through the NA-POPS project \cite{edwards_point_2023}. 
This consists of $712138$ point counts conducted across $292$ projects in Canada and the United States, $422514$ of which used removal sampling and $522820$ of which used distance sampling.

\subsubsection{Phylogenetic Trees}
\par We accessed 2000 pseudo-posterior trees from \citet{jetz_global_2012} that contains phylogeny for all species that contained sufficient data for removal modelling ($>75$ observations as per \cite{edwards_point_2023,solymos_evaluating_2018,buckland_introduction_2001}). 
We also requested that the phylogenies include the following bird species with insufficient data from NA-POPS: LeConte's Thrasher, Bicknell's Thrush, Lesser Prairie-chicken, Harris's Sparrow, Kirtland's Warbler, Tricolored Blackbird, and Spotted Owl. 
All seven of these bird species are listed on Partner's in Flight's watchlist for various threats (CITATION). 
This resulted in 2000 pseudo-posterior trees that contained 323 species.

\par We generated a phylogenetic correlation matrix using the same methods outlined in the Appendix of \citet{solymos_phylogeny_2018} that generate distances between species, and further processed using the R package "ape" \citet{paradis_ape_2019}.

\subsubsection{Species Traits}
\par Species traits (song pitch, migratory vs resident, open vs. closed habitat) were obtained from Birds of the World accounts of all the birds to model in this study (CITATION). 
Body mass for each bird species was obtained form the Elton traits dataset (CITATION). 
Where body mass was not available through the Elton traits dataset, the Birds of the World account was used instead.

\subsection{Bayesian Hierarchical Models}

@@

\subsubsection{Bayesian Hierarchical QPAD Removal Model}

@@

\subsubsection{Bayesian Hierarchical QPAD Distance Model}

@@

\subsection{Model Assessment}
